Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI$\,$837: A Young Validated Planet in IC~2602

### 2020-07-21 paper/ms.tex
Update manuscript

\title{
  Cluster Difference Imaging Photometric Survey (CDIPS) II.
  TOI$\,$837: A Young Validated Saturn-Sized Planet in IC~2602
}

@@

\begin{abstract}
  We report the discovery of TOI 837.01 and its validation as a
  transiting planet.  We characterize the system using data from the
  NASA TESS mission, the ESA Gaia mission, ground-based photometry
  from El Sauce and ASTEP400, and spectroscopy from the CHIRON, FEROS,
  and Veloce spectrographs.  We find that TOI$\,$837 is a $T=9.9$ mag
  G0/F9 dwarf in the southern open cluster IC 2602.  The star
  and planet are therefore $35^{+11}_{-5}$ million years old.
  Combining the transit photometry with a prior on the stellar
  parameters derived from the cluster color-magnitude diagram, we find
  that the planet has an orbital period of $8.3\,{\rm d}$ and is
  slightly smaller than Jupiter ($R_{\rm p} = 0.80^{+0.09}_{-0.03}
  \,R_{\rm Jup}$).  The transits are either grazing or nearly grazing.
  From radial velocity monitoring, we limit the minimum mass to less
  than 1.20 $M_{\rm Jup}$ (3$\sigma$).  Grazing transits are a cause
  for concern, as they are usually indicative of astrophysical false
  positive scenarios.  Our follow-up data show that such scenarios are
  highly unlikely.  Our combined multi-color photometry,
  high-resolution imaging, and radial velocities rule out hierarchical
  eclipsing binary scenarios.  Background eclipsing binary scenarios,
  though limited by speckle imaging, formally remain a 0.2\%
  possibility.  TOI 837.01 is therefore a validated adolescent
  exoplanet.  Further observations of its stellar obliquity,
  atmosphere, and mass should confirm its planetary nature beyond
  doubt, and could improve our understanding of how the physical and
  orbital properties of exoplanets change in time.
\end{abstract}

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f10.png}
	\end{center}
	\vspace{-0.5cm}
	\caption{ 
    {\bf Posterior probabilities of impact parameter, planet-to-star
    size ratio, and stellar density.} 
    Contours are shown at 1, 2, 3, and 4-$\sigma$ confidence.
    The planet-to-star size ratio
    corresponds to a planet size between $0.68\,R_{\rm Jup}$ and
    $0.97\,R_{\rm Jup}$ (3$^{\rm rd}$--97$^{\rm th}$ percentile).
    This plot was made using \texttt{corner} \citep{corner_2016}.
		\label{fig:subsetcorner}
	}
\end{figure}

>>>>

\title{
  Cluster Difference Imaging Photometric Survey (CDIPS) II.
  TOI$\,$837: A Young Validated Planet in IC~2602
}

@@

\begin{abstract}
  We report the discovery of TOI 837.01 and its validation as a
  transiting planet.  We characterize the system using data from the
  NASA TESS mission, the ESA Gaia mission, ground-based photometry
  from El Sauce and ASTEP400, and spectroscopy from CHIRON, FEROS,
  and Veloce.  We find that TOI$\,$837 is a $T=9.9$ mag
  G0/F9 dwarf in the southern open cluster IC 2602.  The star
  and planet are therefore $35^{+11}_{-5}$ million years old.
  Combining the transit photometry with a prior on the stellar
  parameters derived from the cluster color-magnitude diagram, we find
  that the planet has an orbital period of $8.3\,{\rm d}$ and is
  slightly smaller than Jupiter ($R_{\rm p} = 0.80^{+0.09}_{-0.03}
  \,R_{\rm Jup}$).  The transits are either grazing or nearly grazing.
  From radial velocity monitoring, we limit the minimum mass to less
  than 1.20 $M_{\rm Jup}$ (3$\sigma$).  Grazing transits are a cause
  for concern, as they are usually indicative of astrophysical false
  positive scenarios.  Our follow-up data show that such scenarios are
  highly unlikely.  Our combined multi-color photometry,
  high-resolution imaging, and radial velocities rule out hierarchical
  eclipsing binary scenarios.  Background eclipsing binary scenarios,
  though limited by speckle imaging, formally remain a 0.2\%
  possibility.  TOI 837.01 is therefore a validated adolescent
  exoplanet.  Further observations of its stellar obliquity,
  atmosphere, and mass should confirm its planetary nature beyond
  doubt, and could improve our understanding of how the physical and
  orbital properties of exoplanets change in time.
\end{abstract}

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f10.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{ 
    {\bf Posterior probabilities of impact parameter, planet-to-star
    size ratio, and stellar density.} 
    Contours are shown at 1, 2, 3, and 4-$\sigma$ confidence.
    The planet-to-star size ratio
    corresponds to a planet size between $0.68\,R_{\rm Jup}$ and
    $0.97\,R_{\rm Jup}$ (3$^{\rm rd}$--97$^{\rm th}$ percentile).
    This plot was made using \texttt{corner} \citep{corner_2016}.
		\label{fig:subsetcorner}
	}
\end{figure}
